Analysing Constraint Grammars with a SAT-solver

### 2016-03-10 paper/lrec/eval_futurework.tex
changes to future work

The first two variants contain a high number of internal conflicts. 
These are almost all due to nonexisting tags. The grammar was written in 1995, and updated by \newcite{pirinen2015}; such a high number of internal conflicts indicates that possibly something has gone wrong in the conversion, or in our expansion of the morphological lexicon.
As for accuracy, adding the question clitics did not change anything: they were already included in some of the 1588 sets with word forms or lemmas, and that was enough for the SAT-solver to find models with question clitics.
We left the result in the table just to demonstrate the change in the running time.

@@

\subsection{Performance} 
The running time of the grammars ranges from seconds to hours. 
As can be seen from the times, increasing the number of readings
matters more than increasing the number of rules.
In addition, the ambiguity class constraints increase the time.
The times in the Finnish table are not entirely comparable with each other: we were forced to run the tests in smaller batches, and it is possible that there are different overheads, unrelated to the size of the SAT-problem, from testing 50 or 500 rules at a time.

@@

Our solution to hardcode the tag combinations in the readings is
feasible for simple morphology, but it can cause problems with more
complex morphology.
A more scalable solution would be to make each tag a variable, and ask the
question ``can this reading be a noun? how about singular? how about
conditional?'' separately for each tag. Then we could lift the
restriction of tag combinations into a SAT solver: make SAT clauses
that prohibit a comparative to go with a verb, or conditional with a noun.

We are currently working on adding the concepts of lemmas and word
forms directly to the representation of the possible readings.
Currently, if we want to add one more lemma for a verb, we need to
create as many new variables as there are distinct word forms---easily
hundreds for languages with rich morphology.

>>>>

The first two variants reported a high number of internal conflicts. 
These are almost all due to nonexisting tags. The grammar was written in 1995, and updated by \newcite{pirinen2015}; such a high number of internal conflicts indicates that possibly something has gone wrong in the conversion, or in our expansion of the morphological lexicon.
As for accuracy, adding the question clitics did not change anything: they were already included in some of the 1588 sets with word forms or lemmas, and that was enough for the SAT-solver to find models with question clitics.
We left the result in the table just to demonstrate the change in the running time.

@@

\subsection{Performance} 
The running time of the grammars ranges from seconds to hours. 
Note that the times in the Finnish table are not entirely comparable with each other: we were forced to run the tests in smaller batches, and it is possible that there are different overheads, unrelated to the size of the SAT-problem, from testing 50 or 500 rules at a time. 
Despite the inaccuracies, we can see that increasing the number of readings 
and adding the ambiguity class constraints
slow the program down significantly.
%In order to understand the effect of each feature more precisely, we should run our tests on grammars that differ on only one of the variables.

@@

Our solution to hardcode the tag combinations in the readings is
feasible for simple morphology, but it can cause problems with more
complex morphology.
Currently, if we add one new lemma to the set of readings, we need to
create as many new variables as there are inflectional forms
for that lemma. %easily hundreds for languages with rich morphology.

We are currently working on adding the concepts of lemmas and word
forms directly to the representation of the possible readings.
A possible solution would be to make each tag a variable, and ask the
question ``can this reading be a noun? singular? 
conditional?'' separately for each tag. Then we could lift the
restriction of tag combinations into the SAT side: make SAT-clauses
that prohibit a comparative to go with a verb, or conditional with a noun.
Alternatively, we can still hardcode the set of morphological readings, and 
only use SAT-clauses to restrict which lexical form can go with which morphological analysis.
